### 2016-02-09 docs/ms_communitySynchrony.Rmd
removes old commented out text; retrieve here for cached text

Along with environmental fluctuations and interspecific competition, demographic stochasticity can influence synchrony in small populations.
In the absence of all other forces, demographic stochasticity leads to independent species fluctuations and always desynchronizes population dynamics [@Loreau2008a; @DeMazancourt2013a]. 
Interestingly, most previous attempts to decipher the mechanisms behind species synchrony from observational time series relied on a null expectation of independent species fluctuations [e.g., @Houlahan2007].
A null expectation based on demographic stochasticity operating alone is problematic, however, because its affect is strong only in small populations.
In natural communities composed of large populations and exposed to environmental fluctuations and competition, independent species fluctuations should not be expected [@Loreau2008a].
Therefore, inferring the relative importance of competition or the environment based on positive or negative deviations from independent species fluctuations will lead to biased conclusions.
For example, @Houlahan2007 suggested that asynchronous population fluctuations are rare because they found generally positive correlations in species' abundances through time across a large number of ecosystems.
Based on that result and the null expecation that species should fluctuate independently, @Houlahan2007 concluded that abiotic factors synchronize species' abundances.
Thus, if populations are observed to covary positively through time, then the environment must be driving such synchronization.
But, if instead we *a priori* assume that species fluctuate in perfect synchrony [@Loreau2008a], judgment of whether species fluctate synchronously or not depends on the degree to which observed dynamics deviate from perfect synchrony.

@@

<!-- COMMENT THIS OUT FOR NOW...

Our approach has several advantages.
First, we can use the models the directly compare synchrony from communities with and without different processes operating.
This means we do not have to rely on biased null expectations, such as independent species fluctuations, to determine if competition or environmental responses are more important -- we can test for this directly.
Second, our models represent natural communities, rather than experimentally-assembled communities.
This means our results may be more generalizable then results obtained from biodiversity-ecosystem function experiments where strong, but transient, competition is a hallmark [@Gross2014].
Third, our models are based on individual-level demographic data, which allows us to accurately estimate inter and intraspecific competition.
Lastly, we can use the models to estimate the synchrony of species' low density growth rates in the absence of interspecific competition.
Experimental analyses must rely on species' growth in monoculture as an indicator of a species' response to the environemnt, but low density growth rates are a direct measure of a species' immediate response to environmental conditions.
In combination, our dynamic modeling approach represents the most direct means toward unraveling the process that jointly determine community dynamics, species synchrony, and, ultimately, ecosystem stability.

We follow the theory of @Loreau2008a, who show that in a neutral community of *S* species, expected synchrony ($\phi_r$) is defined as:

\begin{equation}
\phi_r = \frac{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(SN)}{[(1/S)(\sum_{i}\sqrt{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(N)})]^2}
\end{equation}

\todo[inline, size=\small]{Claire: I think what we actually want is the non-neutral version here, is there a simple equation for that (something tells me there is not...)?}

\noindent where $\sigma^{2}_{c}$ is the temporal variance of per capita population growth rates due to regulation of community size (density-dependence), $\sigma^{2}_{e}$ is environmental variance, and $\sigma^{2}_{d}$ is demographic variance. *S* is the species richness of the focal community and *N* is the harmonic temporal mean of either the entire community (no subscript in numerator) or species *i* (with subscript in denominator). 
Their analysis isolates three main factors that drive species synchrony in competitive communities: (1) density-dependence via intra- and interspecific competition, (2) environmental fluctuations, and (3) demographic stochasticity.

Loreau and de Mazancourt (2008) show that when demographic stochasticity is weak relative to community regulation and environmental forcing ($\sigma^{2}_{c}+\sigma^{2}_{e} >> \sigma^{2}_{d}/N_i$), $\phi_r \approx \phi_e$, where $phi_e$ is the synchrony of species' responses to the environment. At the other limit, where environmental forcing and community regulation are weak relative to demographic stochasticity ($\sigma^{2}_{c}+\sigma^{2}_{e} << \sigma^{2}_{d}/N_i$), species are expected to fluctuate independently, and $\phi_r \approx 1/S$. 
Based on the theory of @Loreau2008a, we aimed to test the following four hypotheses and associated predictions related to the synchrony of per capita growth rates:

1. Interspecific interactions synchronize population dynamics. Therefore, removing interspecific interactions will decrease synchrony.
2. Plant species in semiarid ecosystems should respond in similar ways to environmental drivers. Therefore, removing environmental variation will decrease synchrony relative to situations were environmental variation is present.
3. In populations small enough for demographic stochasticity to influence dynamics (where $\sigma^{2}_{d} \neq 0$), synchrony will equal the inverse of the number of species in the community (1/*S*), in the absence of species interactions and environmental variation ($\sigma^{2}_{c}$ and $\sigma^{2}_{e} \approx 0$).
4. The de-synchronizing effect of demographic stochasticity will weaken as population size increases, regardless of presence of interspecific interactions or environmental stochasticity.

To test these hypotheses we parameterize and simulate dynamic multi-species population models fit long term demographic data from five semi-arid grasslands [@Chu2015].
We ran simulations directly testing the above hypotheses using a spatially-implicit integral projection model (IPM, hypothesis 1) and a spatially-explicit individual-based model (IBM, hypotheses 2-4).
Our modeling approach allows us to draw inference from real ecological systems that would otherwise be impossible using strictly statistical [e.g., @Mutshinda2009], experimental [e.g., @Gross2014], or observational [e.g., @Houlahan2007] approaches.
Given that our models capture the essential features of community dynamics important to synchrony (density-dependence, demographic and environmental stochasticity) and that these models are able to reproduce observed plant abundances [@Chu2015], perturbing the models according to each hypothesis should reveal the processes responsible for the degree of species synchrony in our focal grassland communities.

Asynchrony in population dynamics (also called compensatory dynamics) among interacting species is a key mechanism by which biodiversity can stabilize aggregate community or ecosystem function [@Ives2002; @Gonzalez2009; @Loreau2010; @Loreau2013].
Experimental work in grassland communities provides strong evidence for the stabilizing effect of asynchronous population dynamics [@Hector2010; @DeMazancourt2013a; @Gross2014; @Hautier2014], but identifying what drives species synchrony in natural communities remains a challenge [@Loreau2008a; @Gonzalez2009; @Loreau2013].
The challenge lies in partitioning community synchrony among three mechanistic drivers of population fluctuations: inter and intraspecific density-dependence, environmental stochasticity, and demographic stochastcity [@Loreau2008a].
Ideally, each mechanism would produce a unique signature on community dynamics and we could infer mechanism by comparing observed synchrony to some null expectation [e.g., @Houlahan2007].
Unfortunately, theoretical work suggests there is no null expectation of community synchrony and the drivers of synchrony interact in complex ways that preclude inference from observations alone [@Loreau2008a; @Loreau2013].

The null expectation for species synchrony has previously been defined as independent species fluctuations.
Such a null is convenient because it allows the use of summed community covariance to infer whether competition or environmental forces drive community dynamics: if summed covariance is negative, then competition is most important; if summed covariance is positive, then environmental forces are most important [@Houlahan2007].
However, independent species fluctuations is only expected under very specific conditions where demographic stochasticity alone is operating and all species have similar growth rates and density-dependence [@Loreau2008a; @Loreau2013].
Likewise, values of summed covariance are not exclusive to particular combinations of drivers, meaning that negative summed covariances can occur in the absence of competition [@Ranta2008].
Finally, summed covariances have no upper or lower limits and are sensitive to community size, making it difficult to compare different communities [@Loreau2008a].
In the end, the fact that few communities exhibit negative summed covariance [e.g., @Houlahan2007] yields little insight on the relative influence of competition and environmental forcing on community dynamics [@Loreau2010].

Theory identifies several limiting cases [@Loreau2008a], but none can be considered an expectation in natural communities where the strengths of internal and external forces are unkown.
For example, independent species fluctuations are expected if only demographic stochasticity if operating and species all have the same abundances and variance [@Loreau2008a].
Furthermore, asymmetry in species' growth rates, competitive effects, and density-dependence can all interact, making it difficult to identify general trends between synchrony and its drivers.
For example, competition generally, but not always, has a positive effect on synchrony of per capita growth rates and a negative effect on synchrony of abundances [@Loreau2013].
Since the mechanisms behind community synchrony are context-dependent, the best way forward is to analyze the drivers of synchrony in natural communities and then relate observed synchrony back to limiting theoretical cases.
In so doing, we can discover common and rare theoretical cases in nature.

Futhermore, analyses of observational time series tend to report synchronous, rather than asynchronous, population dynamics among species of similar ecology [@Houlahan2007; @Mutshinda2009; @Rocha2011; @Vasseur2014].
Thus, our understanding of the prevalence and drivers of asynchronous population dynamics is limited.
Only by fully understanding the mechanisms that lead to asynchronous, or synchronous, dynamics in natural ecosystems can we predict how future biodiversity loss may impact ecosystem functioning [@Loreau2010].

A major roadblock to understanding community synchrony is that many proposed mechanisms lead to similar outcomes.
Asynchronous fluctuations in species' abundances can result from interspecific competition [@Tilman2000] or species-specific responses to variable environmental conditions [@Loreau2013].
However, the effects of interspecific competition and environmental fluctuations are not as general as they appear.
For example, interspecific competition can have either a positive or negative effect on synchrony depending on how strongly species interact, the symmetry of those interactions, and species' growth rates [@Loreau2013].
Likewise, environmental fluctuations can have either a positive or negative effect on synchrony depending on how similarly species respond to environmental conditions.
Since predictions arising from the above mechanisms are not mutually exclusive [@Ranta2008], it is difficult to infer mechanism from population time series [e.g., @Houlahan2007].

Inferring the mechanism driving synchrony in observed population time series has also been hampered by the widespread use of summed community covariance as a metric for detecting compensatory dynamics [e.g., @Ives1995; @Klug2000; @Fischer2001; @Houlahan2007].
The idea is that if the summed covariances of species' abundances through time are positive, then abiotic forces structure dynamics since species covar positively through time in response to a shared environmental driver.
Alternatively, negative summed covariance should indicate that competition structures community fluctuations by driving compensatory dynamics.
Unfortunately, reliance on such a metric created the search for binary states -- synchronous or not, compensatory dynamics or not -- where a continuum exists [@Loreau2008a; @Gross2014].
Likewise, values of summed covariance are not exclusive to particular combinations of drivers, meaning that negative summed covariances can occur in the absence of competition [@Ranta2008].

However, recent theory [@Loreau2008a; @Loreau2013] suggests that previous interpretations of time series have been impaired by (1) a faulty metric of synchrony that treated synchrony and asynchrony as binary states, (2) biased null expectations of species synchrony, and (3) the use of population abundances that are strongly influenced by lag effects and drift to estimate immediate responses to the environment and competition.

How should synchrony be measured?
Traditionally, most researchers relied on summed covariances to detect compensatory, and thus asynchronous, dynamics [e.g., @Ives1995; @Klug2000; @Fischer2001; @Houlahan2007].

To overcome many of these limitations, @Loreau2008a derived a new metric of species synchrony based on a multi-species population dynamic model.
Their proposed metric, which can be applied to per capita growth rates and abundances, is

\begin{equation}
\phi_r = \frac{\sigma^{2}_{T}}{(\sum_{i}\sigma_{x_{i}})^{2}}
\end{equation}

\noindent where $\sigma_{x_{i}}$ is the temporal variance of species *i*'s per capita population growth rate ($r_i$) or abundance ($N_i$) and $\sigma^{2}_{T}$ is the temporal variance of the aggregate community-level growth rate or abundance. 
The metric of @Loreau2008a makes clear that synchrony and asynchrony are not binary states, contrary to their common usage in the literature.
Rather, the synchrony of community dynamics lies along a continuum from perfect asynchrony ($\phi=0$) to perfect synchrony ($\phi=1$).
Thus, our focus should not be on whether or not (a)synchronous dynamics occur, but instead on the degree of (a)synchrony within a community and what process increase or decrease sychrony [e.g., @Gross2014].

What is the null expectation of species synchrony in competitive communities?
Unfortunately, there is not a single answer.
The use of summed community covariance relied on the null expectation that species fluctuate independently [@Ranta2008], which need not be the case [@Loreau2008a; @Loreau2010].

For example, 
Theoretical work has isolated three main factors that drive species synchrony in competitive communities: density-dependence via intra- and interspecific competition, environmental fluctuations, and demographic stochasticity [@Loreau2008a; @Loreau2013].

@Loreau2008a suggest there are two expectations: perfect synchrony in neutral communities where species have identical niches, and the inverse of the number of species in the community (1/*S*) when species fluctuate independently.
Many previous investigations of community synchrony have implicitly assumped that species will fluctuate independently in the absence of temporal niche differences and that strong interspecific interactions cause compensatory dynamics.
For example, @Houlahan2007 suggested that asynchronous population fluctuations are rare because they found generally positive correlations in species' abundances through time across a large number of ecosystems.
Based on that result, @Houlahan2007 concluded that abiotic factors synchronize species' abundances.
However, their null expectation was that species should fluctuate independently.
Thus, if populations are observed to covary positively through time, then the environment must be driving such synchronization.
But, if instead we *a priori* assume that species fluctuate in perfect synchrony [@Loreau2008a], judgment of whether species fluctate synchronously or not depends on the degree to which observed dynamics deviate from perfect synchrony.
Investigations of community synchrony should therefore focus on both endpoints (1 and 1/*S*) and seek to determine the underlying forces that drive synchrony closer to 1 or 1/*S*.

What temporal variable should we use to measure synchrony?
In constrast to virtually every study on synchrony that uses population abundance [e.g., @Houlahan2007; @Mutshinda2009; @Hector2010; @Gross2014; @Vasseur2014], @Loreau2008a suggest community-wide synchrony is best viewed through the lense of per capita growth rates.
On conceptual grounds, per capita growth rates represent the immediate response of species to the environment and competition that we wish to attribute to synchrony.
On practical grounds, positively covarying abundances and negatively covarying environmental responses are not mutually exclusive [@Loreau2008a; @Ranta2008].
Therefore, measuring the synchrony of population abundances through time does not allow inference on the drivers of synchrony.

Aside from issues on how to measure synchrony, disentangling the factors that drive species synchrony is difficult.
Observational timeseries of species' abundances allows easy quantification of summed covariances [@Houlahan2007] or species synchrony [@Gross2014], but quantifying the relative influence of density-dependence, demographic stochasticity, and environmental stochasticity remains a challenge.
Indeed, to our knowledge, only one study has attempted to separate the influences of density-dependence and environmental stochasticity directly [@Mutshinda2009].
@Mutshinda2009 used a statistical technique to decompose synchrony of species' abundances calculated from five time series.
They found that the effect of environmental forcing on temporal dynamics is much stronger than that of interspecific interactions, across all taxa they analyzed [@Mutshinda2009].
However, the @Mutshinda2009 study did not include data from plant communities that have, so far, received the most evidence for a strong role for interspecific interactions in determining species synchrony [@Gross2014].

-->

@@

\begin{equation}
\text{E}(\phi_r) = \frac{1}{\left(\sum_{i}p_{i}^{1/2}\right)^{2}}
\end{equation}

\noindent where $p_i$ is the average frequency of species *i* ($p_i = N_i/N_Total$).

>>>>

Along with environmental fluctuations and interspecific competition, demographic stochasticity can influence synchrony in small populations.
In the absence of all other forces, demographic stochasticity leads to independent species fluctuations and always desynchronizes population dynamics [@Loreau2008a; @DeMazancourt2013a]. 
Interestingly, most previous attempts to decipher the mechanisms behind species synchrony from observational time series relied on a null expectation of independent species fluctuations [e.g., @Houlahan2007].
A null expectation based on demographic stochasticity operating alone is problematic, however, because its effect is strong only in small populations.
In natural communities composed of large populations and exposed to environmental fluctuations and competition, independent species fluctuations should not be expected [@Loreau2008a].
Therefore, inferring the relative importance of competition or the environment based on positive or negative deviations from independent species fluctuations will lead to biased conclusions.
For example, @Houlahan2007 suggested that asynchronous population fluctuations are rare because they found generally positive correlations in species' abundances through time across a large number of ecosystems.
Based on that result and the null expecation that species should fluctuate independently, @Houlahan2007 concluded that abiotic factors synchronize species' abundances.
Thus, if populations are observed to covary positively through time, then the environment must be driving such synchronization.
But, if instead we *a priori* assume that species fluctuate in perfect synchrony [@Loreau2008a], judgment of whether species fluctate synchronously or not depends on the degree to which observed dynamics deviate from perfect synchrony.

@@

@@

\begin{equation}
\text{E}(\phi_N) = \frac{1}{\left(\sum_{i}p_{i}^{1/2}\right)^{2}}
\end{equation}

\noindent where $p_i$ is the average frequency of species *i* ($p_i = N_i/N_{Total}$).
